A thermodynamic view of dusty protoplanetary disks

### 2017-05-17 linear.tex
updated SI table, now do full comparison
improved table 1 format
added bonus figure of comparing SI in two-fluid and one fluid

%"generalized stokes number" would include other problem parameters,
%e.g. wavenumber

@@

\begin{deluxetable*}{llrrrrrr}
  \tablecolumns{8}
  \tablecaption{Selected eigenfrequencies for the streaming
    instability. \label{si_compare}
  }
  \tablehead{
    \colhead{Mode} & 
    \colhead{$\tau_\mathrm{s}\OmK$} &
    \colhead{$\epsilon$} &
     \colhead{$K_{x,z}$} &
      \colhead{$\sigma/\OmK$ (two-fluid)} &
    \colhead{$\sigma/\OmK$ (one-fluid)} &
    \colhead{$\mathcal{W}$ (arbitrary units)} &
      \colhead{$\Delta P$ lag}
  }
\startdata
 linA, \cite{youdin07b} &  $0.1$       & 3.0 & 30    & $0.3480 +
 0.4190\ii$ & $0.3640 + 0.4249\ii$ & $0.90$ & $30\degr$\\

linB, \cite{youdin07b} & $0.1$        &  0.2 & 6 & $-0.4999 +
0.0155\ii$&   $-0.4981 + 0.0054\ii$  & $1.54$ & $1.2\degr$ \\

linC,  \cite{bai10b}  & $10^{-2}$   &  2.0 & 1500&   $0.1049 +
0.5981\ii$   &  $0.1338 + 0.6650\ii$  & $0.15$& $11\degr$ \\

linD, \cite{bai10b} &  $10^{-3}$   &  2.0 & 2000 & $0.3225 + 
0.3154\ii$& $0.3219 + 0.3154\ii$ &  $1.28$ & $22\degr$ 
\enddata
\end{deluxetable*}

>>>>

\begin{figure}
\includegraphics[width=linewidth]{figures/si_2f_1f_compare}
\caption{{\bf in case the paper isn't long enough} Comparison of the linear
streaming instability obtained from a full two-fluid analysis and the current 
one-fluid framework simplified by the terminal velocity approximation. The vertical
wavenumber is fixed and growth rates are maximized over $K_x$. 
\label{si_compare}}
\end{figure}
%"generalized stokes number" would include other problem parameters,
%e.g. wavenumber

@@

% \begin{deluxetable*}{llrrrrrr}
%   \tablecolumns{8}
%   \tablecaption{Selected eigenfrequencies for the streaming
%     instability. \label{si_compare}
%   }
%   \tablehead{
%     \colhead{Mode} & 
%     \colhead{$\tau_\mathrm{s}\OmK$} &
%     \colhead{$\epsilon$} &
%      \colhead{$K_{x,z}$} &
%       \colhead{$\sigma/\OmK$ (two-fluid)} &
%     \colhead{$\sigma/\OmK$ (one-fluid)} &
%     \colhead{$\mathcal{W}$ (arbitrary units)} &
%       \colhead{$\Delta P$ lag}
%   }
% \startdata
%  linA, \cite{youdin07b} &  $0.1$       & 3.0 & 30    & $0.3480 +
%  0.4190\ii$ & $0.3640 + 0.4249\ii$ & $0.90$ & $30\degr$\\

% linB, \cite{youdin07b} & $0.1$        &  0.2 & 6 & $-0.4999 +
% 0.0155\ii$&   $-0.4981 + 0.0054\ii$  & $1.54$ & $1.2\degr$ \\

% linC,  \cite{bai10b}  & $10^{-2}$   &  2.0 & 1500&   $0.1049 +
% 0.5981\ii$   &  $0.1338 + 0.6650\ii$  & $0.15$& $11\degr$ \\

% linD, \cite{bai10b} &  $10^{-3}$   &  2.0 & 2000 & $0.3225 + 
% 0.3154\ii$& $0.3219 + 0.3154\ii$ &  $1.28$ & $22\degr$ 
% \enddata
% \end{deluxetable*}

\begin{deluxetable*}{lrrrrrr}
  \tablecolumns{8}
  \tablecaption{Selected modes of the streaming
    instability. \label{si_compare}
  }
%  \tablehead{
%    \colhead{Mode} & 
%    \colhead{$\tau_\mathrm{s}\OmK$} &
%    \colhead{$\epsilon$} &
%     \colhead{$K_{x,z}$} &
%    \colhead{Complex frequency} &
%    \colhead{$\sigma/\OmK$} &
%    \colhead{Work done} &
%    \colhead{$\mathcal{W}/\left|\Delta P\Delta\rho^*/\rho\right|$} &
%    \colhead{Pressure-density lag} &
%    \colhead{$\varphi$} 
%  }
\startdata
\hline\hline
\multicolumn{1}{c}{Mode ($\tau_\mathrm{s}\OmK$, $K_{x,z}, \rhog/\rhod$)} &
\multicolumn{2}{c}{Complex frequency, $\sigma/\OmK$} &
\multicolumn{2}{c}{Work done, $\mathcal{W}/\left|\Delta P\Delta\rho^*/\rho\right|$} &
\multicolumn{2}{c}{Pressure-density lag, $\varphi$} \\
\hline
\multicolumn{1}{c}{} &
 \multicolumn{1}{c}{two-fluid} &
 \multicolumn{1}{c}{one-fluid} &
 \multicolumn{1}{c}{two-fluid} &
 \multicolumn{1}{r}{one-fluid} &
 \multicolumn{1}{c}{two-fluid} &
 \multicolumn{1}{r}{one-fluid} \\
 \hline
% \multicolumn{6}{c}{\textcolor{blue}{linA\tablenotemark{$\dagger$}: $\tau_\mathrm{s}\OmK=0.1$, $K_{x,z}=30$, $\rhog/\rhod = 3$}}\\
% \hline
linA\tablenotemark{$\dagger$} ($0.1, 30, 3$) &
$0.3480 + 0.4190\ii$ & $0.3640 + 0.4249\ii$ & $0.078$ & $0.090$ & $27\degr$ & $30\degr$  \\
% \hline
% \multicolumn{6}{c}{\textcolor{blue}{linB\tablenotemark{$\dagger$}: $\tau_\mathrm{s}\OmK=0.1$, $K_{x,z}=6$, $\rhog/\rhod = 0.2$}} \\
% \hline
linB\tablenotemark{$\dagger$} ($0.1, 6,0.2$) &
$-0.4999 + 0.0155\ii$&   $-0.4981 + 0.0054\ii$ & 0.025   & $0.0054$ & $5.8\degr$  &  $1.2\degr$  \\
% \hline
% \multicolumn{6}{c}{\textcolor{blue}{linC\tablenotemark{$\ddagger$}: $\tau_\mathrm{s}\OmK=10^{-2}$, $K_{x,z}=1500$, $\rhog/\rhod = 2$}} \\
% \hline
linC\tablenotemark{$\ddagger$} ($10^{-2}, 1500, 2$) &
$0.1049 + 0.5981\ii$   &  $0.1338 + 0.6650\ii$ & 0.0076 & $0.013$ & $8.3\degr$ &$11\degr$  \\
% \hline
% \multicolumn{6}{c}{\textcolor{blue}{linD\tablenotemark{$\ddagger$}: $\tau_\mathrm{s}\OmK=10^{-3}$, $K_{x,z}=2000$, $\rhog/\rhod = 2$}} \\
% \hline
linD\tablenotemark{$\ddagger$} ($10^{-3}, 2000, 2$) &
$0.3225 +  0.3154\ii$& $0.3219 + 0.3154\ii$ &  $0.061$ & $0.061$  & $22\degr$ & $22\degr$  
\enddata
\tablenotetext{$\dagger$}{\cite{youdin07b}}
\tablenotetext{$\ddagger$}{\cite{bai10b}}
\end{deluxetable*}
